Where Do Population III Stars Form?

### 2019-03-29 paper.tex
Adding summary of my thoughts on streaming velocities

@@

>>>>

\noindent\textbf{JHW summary:} We should emphasize your last point for Schauer+ -- that we are overestimating the LW flux in the box.

@@

\noindent\textbf{JHW summary:} Streaming velocities impact the very earliest Pop III host halos because they decrease with the scale factor.  They delay the formation by increasing the necessary halo mass to overcome the bulk velocity.  Just like the studies on LW radiation feedback, the simulations only focus on a handful of halos, whereas, Naoz+ gives a good estimate of the minimum mass (their filtering mass; equations 16-18).  These masses are $2-3 \times 10^5 M_\odot$ and should only be important when the LW flux is small and not suppressing cooling.  All of the halos in our simulation are more massive than this filtering mass.  Even if we included streaming velocities, the gas would've fallen into the potential well when the halo exceeds the filtering mass.  But then it couldn't cool because of the LW background.  Thus I don't think streaming velocities would affect our results much at all.
